---
title: "Revisitng R (Extroverts and productivity)"
author: "Belle Joy Stevens"
date: '2022-05-18'
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

## Extrovert Rating

The extrovert status makes a little difference in revenue and overall productivity 

```{r}
library(readr)
project <- read_csv("C:/Users/belle/OneDrive/Desktop/Analytics/project.txt")
library(tidyverse)
glimpse(project)
library(reader)
install.packages("reader")
library(reader)
glimpse(project)
qplot(extrovert, revenue, data = project)
```

Generic qqplots are not very detailed. Lets try boxplots

```{r}
qplot(extrovert, revenue, data = project, geom = 'boxplot')
```

This gives you an idea about the median and being an extrovert is'nt doing much because the distribution above and below the median looks almost the same

Lets replace boxplots with violin graph

```{r}
qplot(extrovert, revenue, data = project, geom = 'violin')
```

This is a little more detailed, the wide area is the median.

Using other useful functions of R like mean, median and group_by (their education levels), filter (in this case filtering employees with no prior experience)

```{r}
project %>% summarize(avg = mean(revenue))
project %>% summarize(avg = mean(revenue), med = median(revenue), count = n())
project %>% group_by(education) %>% summarize(avg = mean(revenue), med = median(revenue), count = n())
no_prior = project %>% filter(prior_sales == 0)
```

Next, we find the quantiles and bottom and top employees and find a summary of it

```{r}
q10 = quantile(project$revenue, 0.1)
q10
q90 = quantile(project$revenue, 0.9)
q90
top10 = project %>% filter(revenue >= q90)
top10 = project %>% filter(revenue >= q90)
bottom10 = project %>% filter(revenue <= q10)
top10 = project %>% filter(revenue >= q90)
bottom10
summary(top10)
summary(bottom10)

```

we see that extrovert variable is recognized as character and not a string and that doesnt add any value to the data. Therefore lets add a new row where LOW, MED and HIGH will be strings and lets see how that changes the data

```{r}
ext_levels = c('LOW', 'MED', 'HIGH')
project = project %>% mutate(ext_factors = factor(extrovert, levels = ext_levels))
glimpse(project)
bottom10 = project %>% filter(revenue <= q10)
top10 = project %>% filter(revenue >= q90)
summary(top10)
summary(bottom10)
```

No we can see how well the extroverts are doing when the variable became string. Now lets redo the violin graph. Instead of extrovert we replace with ext_factors on the X-axis

```{r}
qplot(ext_factors, revenue, data = project, geom = 'violin')
```
 
This makes the data much more meaningful